\Large \bf Apropos Replacement : Development of a full text search tool for man pages

### 2012-02-28 apropos_replacement.tex
Fix some grammar

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage{listings}
\usepackage{color}
\usepackage{times}
\usepackage{algpseudocode}
%\usepackage[pdftex]{graphicx}
\lstset{ %
language=sh,
basicstyle=\footnotesize,
numbers=none,
backgroundcolor=\color{white},
showspaces=false,
showstringspaces=false,
showtabs=false,
frame=single,
tabsize=2,
captionpos=b,
breaklines=true,
breakatwhitespace=false,
title=\lstname
}

@@

A lot of research has been done on \textit{tf-idf} weights based ranking
algorithms and various techniques have been proposed over the years. According
to a survey done by \textit{Salton} and \textit{Buckley} in 1988 [21], the
following ranking scheme was found to be most effective:

@@

At this point a fast yet sophisticated ranking algorithm was adopted.
\emph{OKAPI BM25F} [15] is considered one of the most successful probabilistic
models for information retrieval. \emph{Okapi BM25F} is based on \emph{tf-idf}
scheme but it takes into account for the structure of the data. It allows for
separate weights to be assigned for different parts of a structured document to
come up with better relevance rankings. This scheme works very well for man pages
because of their highly structured content. The algorithm is described in pseudo-code below. \textit{apropos} calls this function for each of the document
obtained as part of the result set for the query and computes its relevancy
weight. The documents are ranked in decreasing order or the weights returned
from this function. \\

In the following algorithm: \\
{\tt
\lstset{language = sh, caption={},}
\begin{lstlisting}
nhitcount =  Number of occurrences of
             phrase p in column c in
             current document

@@

ndocshitcount = Number of documents in
                which phrase p occurs
                in column c, at least
                once.
\end{lstlisting}
}

\begin{algorithmic}
\State ${\tt tf} \gets 0.0$
\State ${\tt idf} \gets 0.0$
\State ${\tt k} \gets 3.5$
\Comment 
{k is an experimentally determined parameter}
\State ${\tt doclen} \gets $ length of the current document
\State ${\tt ndoc} \gets $ Total number of documents in the corpus
\For {each phrase {\tt p} in the user query}
\For {each column {\tt c} in the FTS table}
\State $w \gets $ weight for column {\tt c}
\State $idf \gets idf + $ $log(\frac{ndoc}{ndocshitcount})\times w $
\State $tf \gets tf + \frac{(nhitcount \times w)}{(nglobalhitcount \times doclen)}$
\EndFor
\EndFor
\State $score \gets $ $\frac{(tf \times idf)}{(k + tf)}$ \\
\Return $score$
\end{algorithmic}

\end{description}
\section{Results}
This section shows results of some of the sample queries on new \textit{apropos}
to demonstrate how it performs as compared to the traditional version.
\endnote{Although this implementation of \textit{apropos} by default returns 10
results for a query but in the following listings the output has been
snipped to save space
} \\

@@

\begin{description}
\item[mandocdb] \hfill \\
\textit{mandocdb} [12] is more in line with the goals of this project but it
takes a novel approach. It indexes the keywords extracted from the man pages in a
key-value store using btree(3) [13]. It also comes with its own implementation
of \textit{apropos} which performs search using this key-value store. The
main key point of this implementation is that it exploits the semantic structure
but rather than indexing the complete content, it plucks out specific pieces of
information from the man pages, for example Author names, function names,
header file names, etc.
from the man pages. It is more sophisticated and much more useful than classic
\textit{apropos}, but it is still essentially a keyword lookup based
implementation.
\end{description}

\section{Future Work}
\begin{description}
\item[Work on Ranking Algorithm] \hfill \\
The ranking algorithm is based on the probabilistic model of information
retrieval [14]results. It
uses certain parameters whose values are usually dependent on the corpus and the
search application. For example, certain weight parameters have been assigned to
different sections of man pages, signifying how important the information in a
particular section is as compared to the rest of the sections. At the moment
these values have been determined
manually but one goal is to use some supervised machine learning techniques in
order to automate this so that more better search results can be obtained.
\end{description}

@@

\bibitem{3}
Brin, S.; Page L.
\emph{The Anatomy of a Large-Scale Hypertextual Web Search Engine}
Computer Networks and ISDN Systems
30:107-117, 1998
\bibitem{4}
Manning; Raghwan; Schutze
\emph{Introduction to information retrieval},
3-9,
2008
\bibitem{5}
Porter, M. F.
\emph{An algorithm for suffix stripping},
Program,
14(3): 130-137,
1980

@@

\bibitem{19}
Jones, Sparck K.
\emph {A statistical interpretation of term specificity and its application in retrieval.}
Journal of Documentation
Volume 28 Number 1 1972 pp. 11-21
\newline
{\tt
http://mdocml.bsd.lv
}

>>>>

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage{listings}
\usepackage{color}
\usepackage{times}
\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
%\usepackage[pdftex]{graphicx}
\lstset{ %
language=sh,
basicstyle=\footnotesize,
numbers=none,
backgroundcolor=\color{white},
showspaces=false,
showstringspaces=false,
showtabs=false,
frame=single,
tabsize=2,
captionpos=b,
breaklines=true,
breakatwhitespace=false,
title=\lstname
}

@@

A lot of research has been done on \textit{tf-idf} weights based ranking
algorithms and various techniques have been proposed over the years. According
to a survey done by \textit{Salton} and \textit{Buckley} in 1988 [20], the
following ranking scheme was found to be most effective:

@@

At this point a fast yet sophisticated ranking algorithm was adopted.
\emph{Okapi BM25F} [15] is considered one of the most successful probabilistic
models for information retrieval. \emph{Okapi BM25F} is based on \emph{tf-idf}
scheme but it takes into account for the structure of the data. It allows for
separate weights to be assigned for different parts of a structured document to
come up with better relevance rankings. This scheme works very well for man pages
because of their highly structured content. The algorithm is described in pseudo-code below. \textit{apropos} calls this function for each of the document
obtained as part of the result set for the query and computes its relevancy
weight. The documents are ranked in decreasing order of the weights returned
from this function. \\

{\tt
\lstset{language = sh, caption={Definition of important entities used in
algorithm \ref{alg1}},}
\begin{lstlisting}
nhitcount =  Number of occurrences of
             phrase p in column c in
             current document

@@

ndocshitcount = Number of documents in
                which phrase p occurs
                in column c, at least
                once.
\end{lstlisting}
}
\begin{algorithm}
\caption{Compute Relevance Weight of a Document for a Given User Query}
\label{alg1}
\begin{algorithmic}[1]
\Require{User query {\tt q}}
\Require{Document {\tt d} whose weight needs to be computed}
\State ${\tt tf} \gets 0.0$
\State ${\tt idf} \gets 0.0$
\State ${\tt k} \gets 3.5$
\Comment 
{k is an experimentally determined parameter}
\State ${\tt doclen} \gets $ length of the current document
\State ${\tt ndoc} \gets $ Total number of documents in the corpus
\For{each phrase {\tt p} in {\tt q}}
\For {each column {\tt c} in the FTS table}
\State $w \gets $ weight for column {\tt c}
\State $idf \gets idf + $ $log(\frac{ndoc}{ndocshitcount})\times w $
\State $tf \gets tf + \frac{(nhitcount \times w)}{(nglobalhitcount \times doclen)}$
\EndFor
\EndFor
\State $score \gets $ $\frac{(tf \times idf)}{(k + tf)}$ \\
\Return $score$
\end{algorithmic}
\end{algorithm}
\end{description}

\section{Results}
This section shows results of some of the sample queries on new \textit{apropos}
to demonstrate how it performs as compared to the traditional version.
\endnote{Although the new \textit{apropos} by default returns 10
results for a query but in the listings the output has been
snipped to save space
} \\

@@

\begin{description}
\item[mandocdb] \hfill \\
\textit{mandocdb} [12] is more in line with the goals of this project but it
takes a novel approach. It indexes the keywords extracted from the man pages in a
key-value store using btree(3) [13]. It also comes with its own implementation
of \textit{apropos} which performs search using this key-value store. The
main key point of this implementation is that it exploits the semantic structure
but rather than indexing the complete content, it plucks out specific pieces of
information from the man pages, for example author names, function names,
header file names, etc.
from the man pages. It is more sophisticated and much more useful than classic
\textit{apropos}, but it is still essentially a keyword lookup based
implementation.
\end{description}

\section{Future Work}
\begin{description}
\item[Work on Ranking Algorithm] \hfill \\
The ranking algorithm is based on the probabilistic model of information
retrieval [14]. It
uses certain parameters whose values are usually dependent on the corpus and the
search application. For example, certain weight parameters have been assigned to
different sections of man pages, signifying how important the information in a
particular section is as compared to the rest of the sections. At the moment
these values have been determined
manually but one goal is to use some supervised machine learning techniques in
order to automate this to improve the quality of search results further.
\end{description}

@@

\bibitem{3}
Brin, S.; Page L.
\emph{The Anatomy of a Large-Scale Hypertextual Web Search Engine}
Computer Networks and ISDN Systems
30:107-117, 1998

\bibitem{4}
Manning; Raghwan; Schutze
\emph{Introduction to information retrieval},
3-9,
2008

\bibitem{5}
Porter, M. F.
\emph{An algorithm for suffix stripping},
Program,
14(3): 130-137,
1980

@@

\bibitem{19}
Jones, Sparck K.
\emph {A statistical interpretation of term specificity and its application in retrieval.}
Journal of Documentation
Volume 28 Number 1 1972 pp. 11-21

\bibitem{20}
Salton, Gerard; Buckley C.
\emph {Term-Weighting Approaches in Automatic Text Retrieval.}
Information Processing \& Management Vol. 24, No. 5, pp. 513-523,
1988
